### 2023-08-14 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
first draft of new tank-treading behavior

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (magenta) energies for a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}

Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with the same geometry and $Ca=0.25$.
Figure~\ref{fig:RA4} shows  the shape of  
a (a) stiff single-component, (b) floppy single-component, and (c) multicomponent
vesicle at six locations along the stenosis channel. We first consider the three different energies---bending,
tension, and phase---for each of these cases. In
Figure~\ref{fig:Energy}, we plot these energies as a function of the
vesicle's center. As a reminder, the vesicle enters the constriction at
$x=-15$ and exits at $x=15$. Also note that the single-component
vesicles do not have a phase energy. 
%A few general trends can immediately be seen. 
First we observe that, as the vesicle enters the stenosis, it
develops regions of high curvature, and this results in an increase in
the bending energy. Secondly, as the stiff single-component and
multicomponent vesicles reach a steady-state shape near the middle of
the channel, their bending, tension, and phase energies remain nearly
constant from $x=0$ until the end of the stenosis. For the multiple-component vesicle,
this implies that there is no coarsening of lipid phase in the middle of a stenosis.

%This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
Such co-existence of multiple lipid domains in a vesicle under confinement
results in interesting additional physics. 
%
First we note that in Figure~\ref{fig:Energy}(c),
the lipid species coarsens at
three instances, and this results in a decrease in the phase energy.
However, as we mentioned earlier, no coarsening occurs when the vesicle is in the
closely-fitting part of the channel. Each coarsening corresponds either
to two stiff regions overtaking a small floppy region, or to two floppy
regions overtaking a small stiff region. In the first case, a region
that was originally floppy has suddenly become stiff, and this results
in a sudden increase in the bending energy. In the latter case, because
of lipid conservation, the overtaken stiff region must relocate to the
another stiff-floppy interface, and this also results in a sudden
increase in the bending energy. These increases are visible in
Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
in both cases, the vesicle smooths out these new regions of high
curvature, but it takes some time since the diffusion time scale is
several orders of magnitude smaller than the bending relaxation time
scale.

%\begin{figure}
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(a)}{figures/Fig13a.pdf}
%    \subfigimg[width=\textwidth]{(c)}{figures/Fig13c.pdf}
%    \subfigimg[width=\textwidth]{(e)}{figures/Fig13e.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.49\columnwidth}
%    \centering
%    \subfigimg[width=\textwidth]{(b)}{figures/Fig13b.pdf}
%    \subfigimg[width=\textwidth]{(d)}{figures/Fig13d.pdf}
%    \subfigimg[width=\textwidth]{(f)}{figures/Fig13f.pdf}
%  \end{minipage}
%  \caption{\label{fig:Energy} \small The Bending (blue), tension
%  (yellow), and phase (red) energies for a (a/b) single-component
%  vesicle with $b=1$, (c/d) single-component vesicle with $b = 0.55$,
%  and (e/f) multicomponent vesicle. The reduced areas are $\alpha = 0.4$
%  (a/c/e) and $\alpha = 0.6$ (b/d/f).}
%  \todo[inline]{need to redo these plots}
%\end{figure}

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
The four marker points are the Lagrangian points where the tank-treading
velocities are computed, the black dashed line is the center line of the
channel, and the rounded arrow denotes the direction of rotation. The
stiff single-component and multicomponent vesicles are clearly tank
treading. Since the single-component case has a larger difference
between its top and bottom boundary layers, it tank treads faster than
the multicomponent case. In addition, since the top boundary layer is
larger in both cases, they both tank-tread in the same
direction---counterclockwise. In contrast, the floppy single-component
vesicle tank treads in the clockwise direction; note, however, that this
example is still undergoing some deformations, so a constant
tank-treading velocity is not observed.
%When $\alpha = 0.6$, the vesicle undergoes deformations while in the
%stenosis, and a constant tank-treading velocity is not observed

%\begin{figure}
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4NoConc.pdf}
%    \end{minipage}
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp4Conc.pdf}
%    \end{minipage}
%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.4.}
%    \label{fig:EnergyRAp4}
%\end{figure}
%\begin{figure}[H]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConc.pdf}
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6NoConcp55.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \includegraphics[width=\textwidth,trim={4cm 8cm 4cm 8cm}, clip]{figures/EnergiesRAp6Conc.pdf}
%        \vspace{3.5cm}
%    \end{minipage}
%    \caption{Bending (blue), tension (yellow), and phase (red) energies for a single-component vesicle %(left) and a multi-component vesicle (right) with reduced area 0.6.}
%    \label{fig:EnergyRAp6l}
%\end{figure}

%\begin{figure}[h]
%    \centering
%    \subfigimg[width = 0.49\columnwidth]{(a)}{figures/Layer_Size_RAp4.pdf}
%%    \subfigimg[width = 0.49\columnwidth]{(b)}{figures/Layer_Size_RAp6.pdf}
%%    \subfigimg[width = \columnwidth]{(a)}{figures/Fig8a.pdf}\\
%%    \subfigimg[width = \columnwidth]{(b)}{figures/Fig8b.pdf}
%    \caption{\label{fig:lubrication} \small The size of the lubrication
%    layer of a stiff single-component (red), floppy single-component
%    (green), and multicomponent (blue) vesicle passing through stenosis.
%    Solid lines are the layer thickness between the vesicle and the top
%    wall, and dashed lines are the layer thickness between the vesicle
%    and the bottom wall. The reduced area of the vesicles are (a)
%    $\alpha = 0.4$ and (b) $\alpha = 0.6$.}
%\end{figure}

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (magenta), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. Also illustrated is the vesicle shape and the four
  Lagrangian points at the location indicated by the dash line. The
  black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction.}
%\end{figure}
\end{figure*}

>>>>

\begin{figure*}[ht]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/SC_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/SCp55_energy.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/MCp5_energy.pdf}
  \caption{\label{fig:Energy} \small The bending (blue), tension (red),
  and phase (magenta) energies of a (a) stiff single-component, (b)
  floppy single-component, and (c) multicomponent vesicle. The reduced
  area is $\alpha = 0.4$. Note that the single-component vesicles do not
  have a phase energy.} 
\end{figure*}

Next we consider a vesicle with a smaller reduced area $\alpha=0.4$ with
the same geometry and $Ca=0.25$. Figure~\ref{fig:RA4} shows the shape of
a (a) stiff single-component, (b) floppy single-component, and (c)
multicomponent vesicle at six locations along the stenosis channel. We
first consider the three different energies---bending, tension, and
phase---for each example. In Figure~\ref{fig:Energy}, we plot these
energies as a function of the vesicle's center. As a reminder, the
vesicle enters the constriction at $x=-15$ and exits at $x=15$. Also
note that the single-component vesicles do not have a phase energy.  We
observe that, as the vesicle enters the stenosis, it develops regions of
high curvature, and this results in an increase in the bending energy.
As the stiff single-component and multicomponent vesicles reach a
steady-state shape near the middle of the channel, their bending,
tension, and phase energies remain nearly constant from $x=0$ until the
end of the stenosis. For the multiple-component vesicle, this implies
that there is no coarsening of lipid phase parameter in the middle of a
stenosis.

%This corresponds to an arrest of phase coarsening for a vesicle confined in a stenosis.
The coexistence of multiple lipid domains in a vesicle under confinement
results in additional interesting physics. We note that in
Figure~\ref{fig:Energy}(c), the lipid species coarsens at three
instances, and this results in a decrease in the phase energy. However,
as we mentioned earlier, no coarsening occurs when the vesicle is in the
closely-fitting part of the channel. Each coarsening corresponds either
to two stiff regions overtaking a small floppy region, or to two floppy
regions overtaking a small stiff region. In the first case, a region
that was originally floppy has suddenly become stiff, and this results
in a sudden increase in the bending energy. In the latter case, because
of lipid conservation, the overtaken stiff region must relocate to the
another stiff-floppy interface, and this also results in a sudden
increase in the bending energy. These increases are visible in
Figure~\ref{fig:Energy}(c) as small upticks in the blue curve. However,
in both cases, the vesicle smooths out these new regions of high
curvature, but it takes some time since the diffusion time scale is
several orders of magnitude smaller than the bending relaxation time
scale.

A main difference between the two reduced areas is that the vesicles
with smaller reduced area undergo tank-treading motions. As mentioned
earlier, tank-treading occurs when the top and bottom lubrication layers
differ in size. The size of the lubrication layers for all three cases
of the vesicle with reduced area $\alpha = 0.4$ are in the top half of
Figure~\ref{fig:lubricationComposite}. Also included in the bottom of
Figure~\ref{fig:lubricationComposite} are the tank-treading velocities.
The four marker points are the Lagrangian points where the tank-treading
velocities are computed, the black dashed line is the center line of the
channel, and the rounded arrow denotes the direction of rotation. The
stiff single-component and multicomponent vesicles are clearly tank
treading. The direction and speed of the tank-treading depends on the
how much of the vesicle membrane is exposed to positive shear (below the
center line) versus how much is exposed to negative shear (above the
center line). The majority of the membrane of the stiff single-component
and multicomponent vesicles are below the center line, and this results
in a clockwise tank-treading behavior. In contrast, the majority of the
membrane of the floppy single-component vesicle is above the center
line, and the result is counterclockwise tank-treading. In addition, the
tank-treading velocity can be correlated to the percentage of its
membrane that is below the center line. We note, however, that the
floppy single-component vesicle is still undergoing deformations, so the
tangential velocities have not converged to a fixed value.

%Since the single-component case has a larger difference
%between its top and bottom boundary layers, it tank treads faster than
%the multicomponent case. In addition, since the top boundary layer is
%larger in both cases, they both tank-tread in the same
%direction---counterclockwise. In contrast, the floppy single-component
%vesicle tank treads in the clockwise direction; note, however, that this
%example is still undergoing some deformations, so a constant
%tank-treading velocity is not observed.

@@

%\begin{figure}[h]
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(a)}{figures/Fig11c1.pdf}
%        \subfigimg[width=\textwidth]{(c)}{figures/Fig11b1.pdf}
%        \subfigimg[width=\textwidth]{(e)}{figures/Fig11a.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(a)}{figures/TankTreadRAp4Conc.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(c)}{figures/TankTreadRANoConcp55.pdf}
%        % \subfigimg[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{(e)}{figures/TankTreadRAp4NoConc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6Conc.pdf}
%        % \includegraphics[width=\textwidth,trim={3.8cm 8cm 4cm 8cm}, clip]{figures/TankTreadRAp6NoConc.pdf}
%    \end{minipage}
%    \hfill
%    \begin{minipage}{0.49\columnwidth}
%        \centering
%        \subfigimg[width=\textwidth]{(b)}{figures/Fig11c2.pdf}
%        \subfigimg[width=\textwidth]{(d)}{figures/Fig11b2.pdf}
%        \subfigimg[width=\textwidth]{(f)}{figures/Fig11a2.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(b)}{figures/TankTreadRAp4ConcVes.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(d)}{figures/TankTreadRANoConcp55Ves.pdf}
%        % \subfigimg[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{(f)}{figures/TankTreadRAp4NoConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6ConcVes.pdf}
%        % \includegraphics[width=.9\textwidth,trim={4.5cm 8cm 4.5cm 8cm}, clip]{figures/TankTreadRAp6NoConcVes.pdf}
%    \end{minipage}
%    \caption{\small The tangential velocity at four Lagrangian points on a (a) single-component vesicle with $b = 1$ (c) single-component vesicle with $b = 0.55$, and (e) multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all cases. (b/d/f) A corresponding vesicle shape with the Lagrangian points.
%    \label{fig:tankTreadRAp4}}
%\end{figure}
\begin{figure*}[t]
%\begin{figure}[htp]
  \centering
  \subfigimg[width=0.3\linewidth]{(a)}{figures/Layer_Size_RAp4_SC.pdf}
  \subfigimg[width=0.3\linewidth]{(b)}{figures/Layer_Size_RAp4_SCp55.pdf}
  \subfigimg[width=0.3\linewidth]{(c)}{figures/Layer_Size_RAp4_MCp5.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm 0cm,clip=true]{}{figures/TankTreadingFigs_composite_SC.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_SCp55.pdf}
  \subfigimg[width=0.3\linewidth,trim=0cm 6cm 28cm
  0cm,clip=true]{}{figures/TankTreadingFigs_composite_MCp5.pdf}
  \caption{\label{fig:lubricationComposite} \small The lubrication layer
  thicknesses (red and blue), excess pressure (magenta), and
  tank-treading velocity of four Lagrangian points of a (a) stiff
  single-component vesicle, (b) floppy single-component vesicle, and (c)
  multicomponent vesicle. The reduced area is $\alpha = 0.4$ in all
  three cases. Also illustrated is the vesicle shape and the four
  Lagrangian points at the location indicated by the dash line. The
  black dashed line is the center line of the channel, and the arrow
  denotes the tank-treading direction. The percentage of the vesicle
  membrane that is below the center line is (a) \%72, (b) \%44, and (c)
  \%68.}
%\end{figure}
\end{figure*}
